### 2017-10-25 doc/eee_symposium/vpd.tex
added presentation and did analytical work

\title[Your Short Title]{When does VPD drive or reduce ET?}
\author{Adam (with Pierre and Changjie)}
\institute{G-Lab Meeting}
\date{October 20th, 2017}

@@

\section{Introduction}
\begin{frame}{When does VPD drive or reduce ET?}
  \begin{itemize}
  \item \textbf{Hydrometeorologists} would say that an increase in VPD (increase in \textbf{atmospheric demand}) would drive an \textbf{increase in ET}.
  \item However, \textbf{plant physiologists} know that plants have evolved to use stomata to conserve and regulate water use. So \textbf{stomata closure} in response to increases in VPD may \textbf{decrease ET}.
  \end{itemize}
\end{frame}

@@

\begin{frame}{Remove dependence of $ET$ on $A$}
  \cite{Zhou_2016} shows that uWUE:
  \[uWUE = \frac{GPP \cdot \sqrt{D}}{ET}\]
  is conserved across space and time (within PFT).\\
  \medskip
  So we can use uWUE to remove dependence of $g_s$ on $A$:
  \[g_s =  \frac{R \, T}{P} 1.6 \left(1 + \frac{g_1}{\sqrt{D_{s}}}\right) \frac{uWUE \; ET}{c_s \; \sqrt{D}}\]
\end{frame}

>>>>

\title[Your Short Title]{When does VPD drive or reduce ET?}
\author{Adam Massmann,  Pierre Gentine and Changjie Lin}
\institute{EEE Graduate Student Symposium}
\date{October 27th, 2017}

@@

\begin{frame}
  \[\frac{g_{a} \rho}{R* R_{air} \sigma uWUE \left(g_{1} + 1.0 \sqrt{- e_{s} \left(RH - 1.0\right)}\right)^{2} \left(\gamma + \frac{d}{d T} e_{s}\right)} \left(RH - 1.0\right) \left(- R* c_{p} \sigma uWUE \left(g_{1} + 1.0 \sqrt{- e_{s} \left(RH - 1.0\right)}\right)^{2} + 0.3125 R_{air} c_{s} g_{1} \gamma + 0.3125 R_{air} c_{s} \gamma \left(g_{1} + 1.0 \sqrt{- e_{s} \left(RH - 1.0\right)}\right)\right)\]
\end{frame}

\section{Introduction}
\begin{frame}{When does vapor pressure deficit (VPD) drive or reduce evapotranspiration (ET)?}
  \[VPD = (1-RH)\cdot e_s (T)\]
\begin{figure}
  \includegraphics[width=0.25in]{stomata.png}
 \caption{from evolution.berkeley.edu}
\end{figure}

  \begin{itemize}
  \item \textbf{Hydrometeorologists} would say that an increase in VPD (increase in \textbf{atmospheric demand}) would drive an \textbf{increase in ET}.
  \item However, \textbf{plant physiologists} know that plants have evolved to use stomata to conserve and regulate water use. So \textbf{stomata closure} in response to increases in VPD may \textbf{decrease ET}.
  \end{itemize}
\end{frame}

@@

\begin{frame}{Remove dependence of $ET$ on $A$}
  \cite{Zhou_2016} shows that uWUE:
  \[uWUE = \frac{GPP \cdot \sqrt{D}}{ET}\]
  is conserved across space and time (within PFT).\\
  \medskip
  So we can use uWUE to remove dependence of $g_s$ on $A$:
p  \[g_s =  \frac{R \, T}{P} 1.6 \left(1 + \frac{g_1}{\sqrt{D_{s}}}\right) \frac{uWUE \; ET}{c_s \; \sqrt{D}}\]
\end{frame}

### 2017-10-25 doc/paper/vpd_et_paper.tex
added presentation and did analytical work

The Penman-Monteith equation (hereafter PM) estimates ET as a function of atmospheric and land-surface variables:

>>>>

The Penman-Monteith equation (hereafter PM) estimates ET as a function of atmospheric and land-surface variables:
\begin{multline}
   - \frac{g_{a} \rho}{D_{s}^{2} R* R_{air} \sigma uWUE \left(\sqrt{D_{s}} + g_{1}\right)^{2} \left(\Delta + \gamma\right) \left(RH - 1.0\right)} \left(D_{s}^{2} \left(RH - 1\right) - e_{s}^{2} \left(RH - 1.0\right)\right) \left(- R* c_{p} \sigma uWUE \left(\sqrt{D_{s}} + g_{1}\right)^{2} + 0.3125 R_{air} c_{s} g_{1} \gamma + 0.3125 R_{air} c_{s} \gamma \left(\sqrt{D_{s}} + g_{1}\right)\right)
\end{multline}

### 2017-10-25 etc/2017-08-28_VPD_uWUE_notes/explicit.tex
added presentation and did analytical work

Here, $g_{1M}$ has units of kPa$^{0.5}$, $A$ is the net CO$_2$ assimilation rate in $\mu$ mol m$^{-2}$ s$^{-1}$, $c_s$ is the CO$_2$ concentration in ppm (supposed to be at leaf surface). The problem is the $A$ term that we need to get rid of. Also $g_w$ as above has units of mol (air?) m$^{-2}$ s$^{-1}$.

>>>>

Here, $g_{1M}$ has units of kPa$^{0.5}$, $A$ is the net CO$_2$ assimilation rate in $\mu$ mnol m$^{-2}$ s$^{-1}$, $c_s$ is the CO$_2$ concentration in ppm (supposed to be at leaf surface). The problem is the $A$ term that we need to get rid of. Also $g_w$ as above has units of mol (air?) m$^{-2}$ s$^{-1}$.
